Appendix 6: sdmTMB model validation and speed-testing methods

### 2021-12-22 doc/appendix-validation.Rmd
Edit app.

The sdmTMB has a number of validation processes to ensure the code is working as expected. This includes unit testing using the testthat package (REF) embedded within the package. This unit testing validates a large number of model configurations against simulated data and comparable models from other packages. We highlight some model validation in particular in this appendix.

In addition to the validation discussed here, Appendix X contains a comparison with VAST and Appendix Y contains a comparison with INLA/inlabru.

@@

Here, we compare a number of smoother configurations against mgcv. Throughout the section we will turn off spatial random fields so the models should be identical.

@@

Here we compare a model that includes two IID random intercepts against the same model fit via glmmTMB. Again, we will turn off random fields so the models are comparable.

>>>>

The sdmTMB package has a number of validation processes to ensure the code is working as expected. 
This includes unit testing using testthat [@testthat] embedded within the package. 
This unit testing validates a large number of model configurations against simulated data and comparable models from other packages. 
We highlight some model validation in particular in this appendix.

In addition to the validation discussed here, Appendix 5 contains a comparison with VAST and Appendix 4 contains a comparison with INLA/inlabru.

@@

Here, we compare a number of smoother configurations against mgcv [@wood2017a]. 
Throughout the section, we will turn off spatial random fields so the models should be comparable.

@@

Here we compare a model that includes two IID random intercepts against the same model fit via glmmTMB [@brooks2017]. 
Again, we will turn off random fields so the models are comparable.
